Windowed least-squares model reduction for dynamical systems

### 2019-10-06 main.tex
update

Substituting the approximation~\eqref{eq:stapprox1} into the FOM
ODE~\eqref{eq:FOM} yields
\begin{equation}\label{eq:st_fom}
\stbasisDotArg{}{t} \stgenstate =  \velocity(\stbasisArg{}{t} \stgenstate +
	\stateIntercept,t) , \qquad \genstate(0) =\mathbb{P}(\stateFOM(0))(0), \qquad t \in [0,T],
\end{equation}
where 
$\stbasisDot\equiv d\stbasis/d\timeDummy$ and
$\mathbb{P} : \RR{N} \rightarrow \stspaceST$ denotes the
orthogonal $\ell^2$-projection onto the space--time trial subspace, i.e.,
$$
\mathbb{P}:\stateyDiscrete\mapsto\underset{\statey\in\stspaceST}{\text{arg\,min}}\int_0^T\|\stateyDiscrete
- \statey( t)\|_2^2d t.
$$
Space--time projection methods reduce the number of equations in
\eqref{eq:st_fom} to ensure a unique solution exists.
We now outline one such method: space--time least-squares Petrov--Galerkin (ST-LSPG)
projection~\cite{choi_stlspg}. 
While space--time Galerkin projection \KTC{add citations. See our ST-LSPG work
where we have some of these} is another alternative, it does not
associate with any residual minimization principle, and thus we do not discuss
it further.
\subsubsection{Space--Time LSPG projection}  
Analogously to LSPG projection, space--time LSPG projection~\cite{choi_stlspg}
minimizes the (time-discrete) FOM O$\Delta$E residual, but does so over the
entire time domain. 
We first define the space--time discrete residual for linear multistep methods,
\begin{align*}
\residST_{} & \vcentcolon (\stateyDiscreteArg{N_t}, \ldots ,\stateyDiscreteArg{1};\stateFOMIC) \mapsto \begin{bmatrix}
%\frac{\stateyDiscreteArg{N_t} - \stateyDiscreteArg{N_t-1}  }{\Delta t} -  \velocity(\stateyDiscreteArg{N_t}) \\
\residLMSArg{N_t}(\stateyDiscreteArg{N_t};\stateyDiscreteArg{N_t-1},\ldots,\stateyDiscreteArg{N_t - k^{N_t}}) \\ 
%\frac{\stateyDiscreteArg{N_t-1} - \stateFOMDiscreteArg{N_t-2}  }{\Delta t} -  \velocity(\stateyDiscreteArg{N_t-1}) \\
\vdots \\
%\frac{\stateyDiscreteArg{1} - \stateFOMIC }{\Delta t} -  \velocity(\stateyDiscreteArg{1}) \\
\residLMSArg{1}(\stateyDiscreteArg{1}; \stateFOMIC) 
\end{bmatrix}  \\
& \vcentcolon \RR{\fomdim} \otimes \RR{N_t+1} \rightarrow \RR{\fomdim N_t}. 
\end{align*}
For convenience we define the same residual with the generalized coordinates as the inputs,
\begin{align*}
\genresidST_{\text{}} & \vcentcolon (\stgenstatey ;\stateFOMIC) \mapsto \begin{bmatrix}
%\frac{\stateyDiscreteArg{N_t} - \stateyDiscreteArg{N_t-1}  }{\Delta t} -  \velocity(\stateyDiscreteArg{N_t}) \\
\residLMSArg{n}\bigg( \stbasisArg{}{t^{N_t}}\stgenstatey + \stateIntercept; \stbasisArg{}{t^{N_t-1}}\stgenstatey + \stateIntercept ,\ldots,  \stbasisArg{}{t^{N_t-k^{N_t}}}\stgenstatey + \stateIntercept \bigg) \\ 
\vdots \\
\residLMSArg{n}\bigg( \stbasisArg{}{t^1}\stgenstatey + \stateIntercept; \stateFOMIC \bigg) \\ 
\end{bmatrix}  \\
& \vcentcolon \RR{\stdim} \times \RR{N} \rightarrow \RR{\fomdim N_t}. 
\end{align*}
ST-LSPG is defined as,
\begin{equation*}
\stgenstate = \underset{ \stgenstatey }{\text{arg\,min}}|| \lspgWeightingSTArg{\stgenstatey}  \genresidST_{\text{}}(\stgenstatey;\stateFOMIC) ||_2^2, 
\end{equation*}
where $\lspgWeightingSTArg{\cdot} \in \RR{n_{st} \times N N_t}$, with $\stdim \le n_{st} \le N N_t$, is a space--time weighting matrix.

>>>>

Substituting the approximation~\eqref{eq:stapprox1} into the FOM
ODE~\eqref{eq:FOM} yields
\begin{equation}\label{eq:st_fom}
\stbasisDotArg{}{t} \stgenstate =  \velocity(\stbasisArg{}{t} \stgenstate +
	\stateIntercept,t) , \qquad \genstate(0) =\mathbb{P}(\stateFOMIC)(0), \qquad t \in [0,T],
\end{equation}
where 
$\stbasisDot\equiv d\stbasis/d\timeDummy$ and
$\mathbb{P} : \RR{N} \rightarrow \stspaceST$ denotes the
orthogonal $\ell^2$-projection onto the space--time trial subspace, i.e.,
$$
\mathbb{P}:\stateyDiscrete\mapsto\underset{\statey\in\stspaceST}{\text{arg\,min}}\int_0^T\|\stateyDiscrete
- \statey( t)\|_2^2d t.
$$
Space--time projection methods reduce the number of equations in
\eqref{eq:st_fom} to ensure a unique solution exists.
We now outline one such method: space--time least-squares Petrov--Galerkin (ST-LSPG)
projection~\cite{choi_stlspg}. 
While space--time Galerkin projection \KTC{add citations. See our ST-LSPG work
where we have some of these} is another alternative, it does not
associate with any residual minimization principle, and thus we do not discuss
it further.
\subsubsection{Space--time LSPG projection}  
Analogously to LSPG projection, space--time LSPG projection~\cite{choi_stlspg}
minimizes the (time-discrete) FOM O$\Delta$E residual, but does so
using the \spaceTimeAcronym\ subspace and simultaneously minimizes this
residual over all $N_t$ time instances.
We first introduce the full space--time FOM O$\Delta$E residual for linear
multistep methods as
\begin{align*}
\residST_{} & \vcentcolon (\stateyDiscreteArg{1}, \ldots
	,\stateyDiscreteArg{N_t};\stateFOMIC) \mapsto \begin{bmatrix}
\residLMSArg{1}(\stateyDiscreteArg{1}; \stateFOMIC) 
%\frac{\stateyDiscreteArg{N_t} - \stateyDiscreteArg{N_t-1}  }{\Delta t} -  \velocity(\stateyDiscreteArg{N_t}) \\
\\ 
%\frac{\stateyDiscreteArg{N_t-1} - \stateFOMDiscreteArg{N_t-2}  }{\Delta t} -  \velocity(\stateyDiscreteArg{N_t-1}) \\
\vdots \\
%\frac{\stateyDiscreteArg{1} - \stateFOMIC }{\Delta t} -  \velocity(\stateyDiscreteArg{1}) \\
\residLMSArg{N_t}(\stateyDiscreteArg{N_t};\stateyDiscreteArg{N_t-1},\ldots,\stateyDiscreteArg{N_t - k^{N_t}}) \end{bmatrix}  \\
& \vcentcolon \RR{\fomdim} \otimes \RR{N_t+1} \rightarrow \RR{\fomdim N_t},
\end{align*}
and define the counterpart function acting on space--time generalized
coordinates associated with the \spaceTimeAcronym\ subspace:
\begin{align*}
\genresidST_{\text{}} & \vcentcolon (\stgenstatey ;\stateFOMIC) \mapsto \begin{bmatrix}
%\frac{\stateyDiscreteArg{N_t} - \stateyDiscreteArg{N_t-1}  }{\Delta t} -  \velocity(\stateyDiscreteArg{N_t}) \\
\residLMSArg{1}\bigg( \stbasisArg{}{t^1}\stgenstatey + \stateIntercept; \stateFOMIC \bigg)
\\ 
\vdots \\
\residLMSArg{N_t}\bigg( \stbasisArg{}{t^{N_t}}\stgenstatey + \stateIntercept; \stbasisArg{}{t^{N_t-1}}\stgenstatey + \stateIntercept ,\ldots,  \stbasisArg{}{t^{N_t-k^{N_t}}}\stgenstatey + \stateIntercept \bigg)  \\ 
\end{bmatrix}  \\
& \vcentcolon \RR{\stdim} \times \RR{N} \rightarrow \RR{\fomdim N_t}. 
\end{align*}
ST-LSPG is defined as,
\begin{equation*}
\stgenstate = \underset{ \stgenstatey }{\text{arg\,min}}|| \lspgWeightingSTArg{\stgenstatey}  \genresidST_{\text{}}(\stgenstatey;\stateFOMIC) ||_2^2, 
\end{equation*}
where $\lspgWeightingSTArg{\cdot} \in \RR{n_{st} \times N N_t}$, with $\stdim \le n_{st} \le N N_t$, is a space--time weighting matrix.
